Domain Specific Languages and Code Synthesis

### 2014-03-14 paper.tex
Pushing the bibtex file
Section 3 edits

An EDSL is a library in a host language which has the look, feel and semantics of its own language,
customized to a specific problem domain.
Using Haskell's concise syntax, Haskell specifically and the functional programming
community in general have taken the ideas
of EDSLs, which considerably lowered the costs of developing
and maintaining a DSL, and developed many, many of DSL 
which provide higher-level interfaces and abstractions for well-understood systems.
We now look at two examples of DSLs, one for automatically generating test cases for software testing,
and a second for specifying hardware circuit behaviors.

>>>>

An EDSL is a library in a host language which has the look, feel and semantics of its own language,
customized to a specific problem domain.
EDSLs, by reusing the facilities and tools of the host language, considerably lower the cost of developing and maintaining a DSL.
Benefiting from Haskell's concise syntax, the Haskell community, and the functional programming
community in general, have taken the ideas
of EDSLs and developed a large number of DSLs
which provide higher-level interfaces and abstractions for well-understood systems.
We now look at two examples of DSLs, one for automatically generating test cases for software testing,
and a second for specifying hardware circuit behaviors.
